A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Move Garbage collection section in front of Dynamic variable ordering
Add Garbage collection intro

>>>>

The first OBDD package containing kind of a garbage collection was the one
introduced by Brace, Bryant and Rudell~\cite{BRACE90}. The garbage collection was
based upon the reference counting technique, i.e. every node of the OBDD had a
reference count. This reference count represents two kinds of references, (1)
the number of other nodes and (2) the number of formulas referencing it, but does
not take references from the unique- and computed-table into account. \tbr
